--- 
title: "Crime Visualization in New York City"
author: "Zihao Zhang/ Yunshu Cai/ Moya Zhu"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
---
```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```


# Introduction

<!--chapter:end:index.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Data sources

Data source of this project is from 

[NYPD Complaint Data Historic] Provided by Police Department (NYPD)

Link: https://data.cityofnewyork.us/Public-Safety/NYPD-Complaint-Data-Historic/qgea-i56i?ref=hackernoon.com


The dataset has more than 7M rows and each row represents one complaint related to a crime event. 

One complaint contains information related to the accident time, reported time, the event position, the characteristics of victim and suspect. According to the exact date of occurrence for the reported event, the year ranges from 1950 to 2020. We mainly focuses on 2018-2020 data, since it can better represent the most recent trend. 

<!--chapter:end:02-data.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Data transformation

<!--chapter:end:03-cleaning.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Missing values
```{r, echo=FALSE}
# this prevents package loading message from appearing in the rendered version of your problem set
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE,
  echo = TRUE)
library(dplyr)
library(ggplot2)
library(tidyverse)
library(patchwork)
```

## Column pattern

```{r, echo=FALSE}
missing_plot_func <- function(inputdata, option) {
  mycars = inputdata
  n_vars = ncol(mycars)
  n_rows = nrow(mycars)
  if (option == 'counts') {
    #create missing pattern
    missing_patterns <- data.frame(is.na(mycars)) %>%
      group_by_all() %>%
      count(name = "count", sort = TRUE) %>%
      ungroup()
    n_rows = nrow(missing_patterns)
    
    #side plots
    missing.values <- mycars %>%
      select(everything()) %>%  # replace to your needs
      summarise_all(funs(sum(is.na(.)))) %>%
      gather(key = "key", value = "val") %>%
      arrange(desc(val))
    
    s1 <- missing.values %>%
      ggplot() +
      geom_bar(aes(x = reorder(key,-val), y = val), fill = "#f68060", stat = 'identity') +
      labs(x = 'variable', y = "number of missing values", title = 'Missing value pattern') +
      theme(axis.text.x = element_text(angle = 45, hjust = 1))
    
    missing_patterns_withAP <- missing_patterns
    selected <-
      which(apply(missing_patterns[, -length(missing_patterns)], 1, any) == F[1])
    alpha_vector = rep(1, nrow(missing_patterns_withAP))
    alpha_vector[selected] = 2
    missing_patterns_withAP$hl_alpha = alpha_vector
    
    missing_patterns_withAP["id"] <- as.factor(seq(1, n_rows))
    s2_y = fct_reorder(missing_patterns_withAP$id,
                       as.numeric(missing_patterns_withAP$id),
                       .desc = TRUE)
    # s2_y <- factor(s2_y, levels = sort(levels(s2_y), decreasing = TRUE))
    
    s2 <- missing_patterns_withAP %>%
      ggplot() +
      geom_bar(aes(
        x = count,
        fill = "#f68060",
        s2_y,
        alpha = hl_alpha
      ), stat = 'identity') +
      scale_alpha(range = c(0.45, 1)) +
      labs(x = 'row count', y = '') +
      theme(axis.text.x = element_text(angle = 45, hjust = 1),
            legend.position = "none")
    missing_patterns_cleaned <- select(missing_patterns, -count)
    selected <-
      which(apply(missing_patterns[,-length(missing_patterns)], 1, any) == F[1])
  }
  
  if (option == 'percent') {
    missing_patterns <-   data.frame(is.na(mycars)) %>%
      group_by_all() %>%
      count(name = "count", sort = TRUE) %>%
      ungroup() %>%
      mutate(pct = count / nrow(mycars))
    #side 1 col
    missing.values <- mycars %>%
      select(everything()) %>%  # replace to your needs
      summarise_all(funs(sum(is.na(.)))) %>%
      gather(key = "key", value = "val") %>%
      mutate(pct = val / n_rows) %>%
      arrange(desc(pct))
    
    #    print(missing_patterns)
    n_rows = nrow(missing_patterns)
    
    s1 <- missing.values %>%
      ggplot() +
      geom_bar(aes(x = reorder(key,-pct), y = pct), fill = "#f68060", stat = 'identity') +
      labs(x = 'variable', y = "number percentage of missing values", title = 'Missing value pattern') +
      theme(axis.text.x = element_text(angle = 45, hjust = 1))
    #side 2 row
    
    missing_patterns_withAP <- missing_patterns
    selected <-
      which(apply(missing_patterns[1:n_vars], 1, any) == F[1])
    alpha_vector = rep(1, nrow(missing_patterns_withAP))
    alpha_vector[selected] = 2
    missing_patterns_withAP$hl_alpha = alpha_vector
    
    missing_patterns_withAP["id"] <- as.factor(seq(1, n_rows))
    s2_y = fct_reorder(missing_patterns_withAP$id,
                       as.numeric(missing_patterns_withAP$id),
                       .desc = TRUE)
    #  s2_y <- factor(s2_y, levels = sort(levels(s2_y), decreasing = TRUE))
    
    s2 <- missing_patterns_withAP %>%
      ggplot() +
      geom_bar(aes(
        x = pct,
        fill = "#f68060",
        s2_y,
        alpha = hl_alpha
      ), stat = 'identity') +
      scale_alpha(range = c(0.45, 1)) +
      labs(x = 'row percentage', y = '') +
      theme(axis.text.x = element_text(angle = 45, hjust = 1),
            legend.position = "none")
    
    missing_patterns_cleaned <-
      select(missing_patterns, -c(count, pct))
    
    selected <-
      which(apply(missing_patterns[,-c(length(missing_patterns), length(missing_patterns) -
                                         1)], 1, any) == F[1])
    
  }
  #create main plot
  
  missing_patterns_modified <- missing_patterns_cleaned %>%
    rownames_to_column("id") %>%
    gather(key, value, -id) %>%
    mutate(missing = ifelse(value == 1, 1, 0)) %>%
    mutate(missing_patterns[id, "count"])
  
  missing_patterns_merged <-
    merge(x = missing.values,
          y = missing_patterns_modified,
          by = "key",
          all = TRUE)
  
  y =  fct_reorder(missing_patterns_merged$id,
                   as.numeric(missing_patterns_merged$id),
                   .desc = TRUE)
  #y <- factor(y, levels = sort(levels(y), decreasing = TRUE))
  
  #selected <- which(apply(missing_patterns[, -length(missing_patterns)], 1, any) == F[1])
  alpha_vector = rep(1, nrow(missing_patterns_merged))
  highlight <-
    as.vector(which(missing_patterns_merged$id == selected))
  
  alpha_vector[highlight] = 2
  missing_patterns_merged$hl_alpha = alpha_vector
  
  main <-
    ggplot(missing_patterns_merged,
           aes(
             x = fct_reorder(key, val, .desc = TRUE),
             y,
             fill = as.factor(missing),
             alpha = hl_alpha
           )) +
    geom_tile(color = "white") +
    scale_fill_manual(values = c("grey", "mediumpurple")) +
    scale_alpha(range = c(0.45, 1)) +
    theme_bw() +
    labs(x = 'variable', y = "missing pattern") +
    
    theme(legend.position = "none",
          axis.text.x = element_text(angle = 45, hjust = 1))
  
  
  #patchwork plot together
  library(patchwork)
  (s1 + plot_spacer()) /
    (main |
       s2 + plot_spacer()) +  plot_layout(ncol = 1,
                                          width = c(4, 1),
                                          heights = unit(c(1, 5), c('cm', 'null')))
}
```

```{r, echo=FALSE}
data = read.csv('NYPD_Complaint_Data_Historic_2018_2020.csv', na.strings=c("","NA"))
```

After implementing our self-defined missing value plot function here, the plot is shown as below.

```{r, echo=FALSE, fig.height=15, fig.width=30}
data_visna = data
# colnames(data_visna) <- colnames(data_visna) %>% substring(1, 10) 
# # several column names are just too long...
missing_plot_func(data_visna, 'percent')
```

According the plot, we found that variables below have a large ratio of missing values. We put the basic descriptions in corresponding variables:

- PARKS_NM: Name of NYC park, playground or greenspace of occurrence, if applicable (state parks are not included).
- HADEVELOPT: Name of NYCHA housing development of occurrence, if applicable.
- HOUSING_PSA: Development Level Code.
- TRANSIT_DISTRICT: Transit district in which the offense occurred.
- STATION_NAME: Transit station name

The descriptions show that it makes senses that the former 3 variables have missing values since they are all possibly applicable variables, which means that when being designed, it is presumed that there might be no values here.

As the latter two variables, the logic is similar that not every crime event happens near a transit station.

Left missing variables include:

- SUSP_AGE_GROUP,
- SUSP_RACE,
- SUSP_SEX,
- LOC_OF_OCCUR_DESC,
- COMPLNT_TO_DT,
- COMPLNT_TO_TM

The latter three will not be used in our analysis. And as for the suspicion portrait, we decided to exclude them immediately since the proportion is not significant.

<!--chapter:end:04-missing-copy.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Missing values
```{r, echo=FALSE}
# this prevents package loading message from appearing in the rendered version of your problem set
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE,
  echo = TRUE)
library(dplyr)
library(ggplot2)
library(tidyverse)
library(patchwork)
```

## Column pattern

```{r, echo=FALSE}
missing_plot_func <- function(inputdata, option) {
  mycars = inputdata
  n_vars = ncol(mycars)
  n_rows = nrow(mycars)
  if (option == 'counts') {
    #create missing pattern
    missing_patterns <- data.frame(is.na(mycars)) %>%
      group_by_all() %>%
      count(name = "count", sort = TRUE) %>%
      ungroup()
    n_rows = nrow(missing_patterns)
    
    #side plots
    missing.values <- mycars %>%
      select(everything()) %>%  # replace to your needs
      summarise_all(funs(sum(is.na(.)))) %>%
      gather(key = "key", value = "val") %>%
      arrange(desc(val))
    
    s1 <- missing.values %>%
      ggplot() +
      geom_bar(aes(x = reorder(key,-val), y = val), fill = "#f68060", stat = 'identity') +
      labs(x = 'variable', y = "number of missing values", title = 'Missing value pattern') +
      theme(axis.text.x = element_text(angle = 45, hjust = 1))
    
    missing_patterns_withAP <- missing_patterns
    selected <-
      which(apply(missing_patterns[, -length(missing_patterns)], 1, any) == F[1])
    alpha_vector = rep(1, nrow(missing_patterns_withAP))
    alpha_vector[selected] = 2
    missing_patterns_withAP$hl_alpha = alpha_vector
    
    missing_patterns_withAP["id"] <- as.factor(seq(1, n_rows))
    s2_y = fct_reorder(missing_patterns_withAP$id,
                       as.numeric(missing_patterns_withAP$id),
                       .desc = TRUE)
    # s2_y <- factor(s2_y, levels = sort(levels(s2_y), decreasing = TRUE))
    
    s2 <- missing_patterns_withAP %>%
      ggplot() +
      geom_bar(aes(
        x = count,
        fill = "#f68060",
        s2_y,
        alpha = hl_alpha
      ), stat = 'identity') +
      scale_alpha(range = c(0.45, 1)) +
      labs(x = 'row count', y = '') +
      theme(axis.text.x = element_text(angle = 45, hjust = 1),
            legend.position = "none")
    missing_patterns_cleaned <- select(missing_patterns, -count)
    selected <-
      which(apply(missing_patterns[,-length(missing_patterns)], 1, any) == F[1])
  }
  
  if (option == 'percent') {
    missing_patterns <-   data.frame(is.na(mycars)) %>%
      group_by_all() %>%
      count(name = "count", sort = TRUE) %>%
      ungroup() %>%
      mutate(pct = count / nrow(mycars))
    #side 1 col
    missing.values <- mycars %>%
      select(everything()) %>%  # replace to your needs
      summarise_all(funs(sum(is.na(.)))) %>%
      gather(key = "key", value = "val") %>%
      mutate(pct = val / n_rows) %>%
      arrange(desc(pct))
    
    #    print(missing_patterns)
    n_rows = nrow(missing_patterns)
    
    s1 <- missing.values %>%
      ggplot() +
      geom_bar(aes(x = reorder(key,-pct), y = pct), fill = "#f68060", stat = 'identity') +
      labs(x = 'variable', y = "number percentage of missing values", title = 'Missing value pattern') +
      theme(axis.text.x = element_text(angle = 45, hjust = 1))
    #side 2 row
    
    missing_patterns_withAP <- missing_patterns
    selected <-
      which(apply(missing_patterns[1:n_vars], 1, any) == F[1])
    alpha_vector = rep(1, nrow(missing_patterns_withAP))
    alpha_vector[selected] = 2
    missing_patterns_withAP$hl_alpha = alpha_vector
    
    missing_patterns_withAP["id"] <- as.factor(seq(1, n_rows))
    s2_y = fct_reorder(missing_patterns_withAP$id,
                       as.numeric(missing_patterns_withAP$id),
                       .desc = TRUE)
    #  s2_y <- factor(s2_y, levels = sort(levels(s2_y), decreasing = TRUE))
    
    s2 <- missing_patterns_withAP %>%
      ggplot() +
      geom_bar(aes(
        x = pct,
        fill = "#f68060",
        s2_y,
        alpha = hl_alpha
      ), stat = 'identity') +
      scale_alpha(range = c(0.45, 1)) +
      labs(x = 'row percentage', y = '') +
      theme(axis.text.x = element_text(angle = 45, hjust = 1),
            legend.position = "none")
    
    missing_patterns_cleaned <-
      select(missing_patterns, -c(count, pct))
    
    selected <-
      which(apply(missing_patterns[,-c(length(missing_patterns), length(missing_patterns) -
                                         1)], 1, any) == F[1])
    
  }
  #create main plot
  
  missing_patterns_modified <- missing_patterns_cleaned %>%
    rownames_to_column("id") %>%
    gather(key, value, -id) %>%
    mutate(missing = ifelse(value == 1, 1, 0)) %>%
    mutate(missing_patterns[id, "count"])
  
  missing_patterns_merged <-
    merge(x = missing.values,
          y = missing_patterns_modified,
          by = "key",
          all = TRUE)
  
  y =  fct_reorder(missing_patterns_merged$id,
                   as.numeric(missing_patterns_merged$id),
                   .desc = TRUE)
  #y <- factor(y, levels = sort(levels(y), decreasing = TRUE))
  
  #selected <- which(apply(missing_patterns[, -length(missing_patterns)], 1, any) == F[1])
  alpha_vector = rep(1, nrow(missing_patterns_merged))
  highlight <-
    as.vector(which(missing_patterns_merged$id == selected))
  
  alpha_vector[highlight] = 2
  missing_patterns_merged$hl_alpha = alpha_vector
  
  main <-
    ggplot(missing_patterns_merged,
           aes(
             x = fct_reorder(key, val, .desc = TRUE),
             y,
             fill = as.factor(missing),
             alpha = hl_alpha
           )) +
    geom_tile(color = "white") +
    scale_fill_manual(values = c("grey", "mediumpurple")) +
    scale_alpha(range = c(0.45, 1)) +
    theme_bw() +
    labs(x = 'variable', y = "missing pattern") +
    
    theme(legend.position = "none",
          axis.text.x = element_text(angle = 45, hjust = 1))
  
  
  #patchwork plot together
  library(patchwork)
  (s1 + plot_spacer()) /
    (main |
       s2 + plot_spacer()) +  plot_layout(ncol = 1,
                                          width = c(4, 1),
                                          heights = unit(c(1, 5), c('cm', 'null')))
}
```

```{r, echo=FALSE}
data = read.csv('/Users/mac/Downloads/NYPD_Complaint_Data_Historic_2018_2020.csv', na.strings=c("","NA"))
```

After implementing our self-defined missing value plot function here, the plot is shown as below.

```{r, echo=FALSE, fig.height=15, fig.width=30}
data_visna = data
# colnames(data_visna) <- colnames(data_visna) %>% substring(1, 10) 
# # several column names are just too long...
missing_plot_func(data_visna, 'percent')
```

According the plot, we found that variables below have a large ratio of missing values. We put the basic descriptions in corresponding variables:

- PARKS_NM: Name of NYC park, playground or greenspace of occurrence, if applicable (state parks are not included).
- HADEVELOPT: Name of NYCHA housing development of occurrence, if applicable.
- HOUSING_PSA: Development Level Code.
- TRANSIT_DISTRICT: Transit district in which the offense occurred.
- STATION_NAME: Transit station name

The descriptions show that it makes senses that the former 3 variables have missing values since they are all possibly applicable variables, which means that when being designed, it is presumed that there might be no values here.

As the latter two variables, the logic is similar that not every crime event happens near a transit station.

Left missing variables include:

- SUSP_AGE_GROUP,
- SUSP_RACE,
- SUSP_SEX,
- LOC_OF_OCCUR_DESC,
- COMPLNT_TO_DT,
- COMPLNT_TO_TM

The latter three will not be used in our analysis. And as for the suspicion portrait, we decided to exclude them immediately since the proportion is not significant.

<!--chapter:end:04-missing.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Results

<!--chapter:end:05-results.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Interactive component



<!--chapter:end:06-interactive.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Conclusion


<!--chapter:end:07-conclusion.Rmd-->

